\section{Homework 3}
\subsection{Exercise 3.42}
For this problem we have to show that the below function is quasiconcave
\begin{equation}
  W(x) = \sup \{ T | |x_1 f_1(t) + \dots + x_n f_n(t) - f_0(t)| \leq \epsilon \text{ for } 0 \leq t \leq T \}
\end{equation}
To prove this, we can find if for each $\epsilon$, the function is concave. The definition of quasiconcavity is that all its superlevel sets are concave. In order to evaluate the superlevel sets, we can flip the infimum and supremum
\begin{equation}
  W(x) = \inf \{ T | |x_1 f_1(t) + \dots + x_n f_n(t) - f_0(t)| \geq \epsilon \text{ for } 0 \leq t \leq T \}
\end{equation}
This form of the equation now flips the equal sign so we can evaluate the superlevel sets with the threshold being $\epsilon$. The point-wise infimum of a set of concave functions is a concave function. So, as long as the function inside is a concave function, then this holds. The function there is a linear combination of x and therefore it is convex, and therefore quasiconcave.

\subsection{Exercise 3.54}
Verifying log concavity of the the function
\begin{equation}
  f(x) = \frac{1}{\sqrt{2\pi}} \int_{-\infty}^{x} e^\frac{-t^2}{2} dt
\end{equation}
\subsubsection{Part a}
Verifying that $f^{\prime \prime} f(x) \leq f^\prime(x)^2, x \geq 0$
\begin{gather}
  f^\prime(x) = \frac{1}{\sqrt{2\pi}} \frac{d }{d x}  \int_{-\infty}^{x} e^\frac{-t^2}{2} dt \\
  = \frac{1}{\sqrt{2\pi}} e^\frac{-x^2}{2}
\end{gather}

\begin{gather}
  f^{\prime \prime}(x) = \frac{1}{\sqrt{2\pi}} \frac{d }{d x} e^\frac{-x^2}{2} \\
  = - \frac{1}{\sqrt{2\pi}} e^\frac{-x^2}{2}x
\end{gather}

\begin{gather}
  f^{\prime \prime}(x) f(x) \leq f^\prime(x)^2 \\
  - \frac{1}{\sqrt{2\pi}} e^\frac{-x^2}{2}x \frac{1}{\sqrt{2\pi}} \int_{-\infty}^{x} e^\frac{-t^2}{2}dt \leq  (\frac{1}{\sqrt{2\pi}} e^\frac{-x^2}{2})^2 \\
  -e^\frac{-x^2}{2}x \int_{-\infty}^{x} e^\frac{-t^2}{2}dt \leq (e^\frac{-x^2}{2})^2
\end{gather}
If $x= 0$, the inequality $0 \leq 1$ holds. If $x > 0$, the left hand side of the inequality will always be negative and the right hand side will be greater than 1. Therefore the statement $f^{\prime \prime}(x) f(x) \leq f^\prime(x)^2, x \geq 0$ holds.
\subsubsection{Part b}
Verifying that for any $t$ and $x$, we have $\frac{t^2}{2} \geq \frac{-x^2}{2}+xt$
I am not sure the most rigorous way to do this, so I will evaluate the signs of each side on every combation of zero, positive, and negative.
\begin{itemize}
  \item $x=0, t=0 \to 0 \geq 0$ => evidently true since zero equals zero
  \item $x>0 \text{ or } x<0, t=0 \to 0 \geq -\frac{x^2}{2}$ => evidently true since a negative number is lower than zero
  \item $x=0, t>0 \text{ or } t<0 \to \frac{t^2}{2}\geq 0$ => evidently true since a positive number is greater than zero
  \item $x<0, t> 0 \to \frac{t^2}{2} \geq -\frac{x^2}{2} - |x| t$ evidently true since a positive number is greater than a negative number
  \item $x<0, t<0 \to t^2 +x^2 \geq 2|x| |t|$ this is the arithmetic-geometric mean inequality 
\end{itemize}

\subsubsection{Part c}
Part b can be flipped and applying log to both sides we see that $e^\frac{-t^2}{2} \leq e^{\frac{x^2}{2}-xt}$
\begin{gather}
  e^\frac{-t^2}{2} \leq e^{\frac{x^2}{2}-xt} \\
  \int_{-\infty}^{x} e^\frac{-t^2}{2}dt \leq \int_{-\infty}^{x}e^{\frac{x^2}{2}-xt} dt \\ 
  \int_{-\infty}^{x} e^\frac{-t^2}{2}dt \leq e^{\frac{x^2}{2}}\int_{-\infty}^{x}e^{-xt} dt
\end{gather}

\subsubsection{Part d}
\begin{gather}
  \int_{-\infty}^{x} e^\frac{-t^2}{2}dt \leq -e^\frac{-x^2}{2}x 
\end{gather}

\subsection{Exercise 3.57}
Showing that the function $f(X) = X^{-1} $ is matrix convex on $\mathbb{S}_{++}^n$
If the matrix $X$ is positive definite, then its inverse is also positive definite and therefore matrix convex.
\subsection{Exercise 4.4}

\subsection{Exercise 4.8}

\subsection{Exercise 4.17}
